### 2019-01-18 micro3_2.tex
Micro

\section*{Problem 3}
Suppose that for $w = (w_1, w_2) >> 0$, \begin{align*}
a_{11} = \frac{2}{3w_1}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
a_{21} = \frac{2}{3w_2}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
a_{12} = 
\end{align*}
\end{document}

>>>>

\section*{Problem 3}
Suppose that for $w = (w_1, w_2) >> 0$, \begin{align*}
a_{11} = \frac{2}{3w_1}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
a_{21} = \frac{1}{3w_2}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
a_{12} = \frac{1}{3w_1}\left(\frac{w_1}{1/3}\right)^{1/3}\left(\frac{w_2}{2/3}\right)^{2/3}\\
a_{22} = \frac{2}{3w_2}\left(\frac{w_1}{1/3}\right)^{1/3}\left(\frac{w_2}{2/3}\right)^{2/3}\\
\end{align*}
where $a_j(w) := (a_{1j}(w); a_{2j}(w))$ is the conditional factor demand of firm $j$ that corresponds
to one unit of output. Assume $p_1 = p_2 = \frac{1}{2}$. Find the equilibrium factor allocation and
prices as a function of factor endowments $\bar{z_1}; \bar{z_2} > 0$. (Be sure to cover boundary equilibria,
if any.)

Assume $c_1(w), c_2(w)$ are cost functions of firms 1 and 2 for producing 1 unit of output. Then
\begin{align*}
\frac{\partial c_1(w)}{\partial w_1} = a_{11} = \frac{2}{3w_1}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3} \to c_1(w) =\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3} + \varphi(w_2)\\
\end{align*}
where $\varphi(w_2)$ is an arbitrary function of $w_2$.
\begin{align*}
\frac{\partial c_1(w)}{\partial w_2} = \frac{1}{3w_2}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3} + \frac{d\varphi(w_2)}{dw_2} = a_{21} \to \varphi(w_2) = const
\end{align*}
if there are no fixed costs then of course $\varphi(w_2) = 0$. Thus, 
\begin{align*}
c_1(w) = \left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}
\end{align*}
Similarly, 
\begin{align*}
c_2(w) = \left(\frac{w_1}{1/3}\right)^{1/3}\left(\frac{w_2}{2/3}\right)^{2/3}
\end{align*}
Suppose firstly that the equilibrium is interior. Hence
\begin{align*}
\frac{c_1(w)}{c_2(w)} &= \frac{p_1}{p_2}\\
\left(\frac{w_1}{w_2}\right)^{1/3} = 1 &\to w_1 = w_2\\
c_1(w) = p_1 &\to w_1^* = w_2^* = \frac{1}{2^{1/3}3}
\end{align*}
Now let us derive the inferior solution condition.
\begin{align*}
\frac{a_{11}}{a_{21}} &= 2\\
\frac{a_{12}}{a_{22}} &= \frac{1}{2}\\
\end{align*}
\begin{align}\label{eq1}
2 > \frac{\bar{z_1}}{\bar{z_2}} > \frac{1}{2} &\to \frac{\bar{z_2}}{2} < \bar{z_1} < 2\bar{z_2}
\end{align}
Market clearing conditions:
\begin{align*}
q_1 a_1(w) + q_2 a_2(w) = \bar{z}\\
q_1 \begin{pmatrix}
2^{1/3}\\
\frac{1}{2^{2/3}}
\end{pmatrix} + q_2 \begin{pmatrix}
\frac{1}{2^{2/3}}\\
2^{1/3}
\end{pmatrix} = \begin{pmatrix}
\bar{z_1}\\
\bar{z_2}
\end{pmatrix}\\
q_2^* = \frac{2\bar{z_2} - \bar{z_1}}{4 - \frac{1}{2^{2/3}}}, q_1^* = \frac{\bar{z_1}}{2^{1/3}} - \frac{2\bar{z_2} - \bar{z_1}}{8 - 2^{1/3}}
\end{align*}
One can easily check that under \eqref{eq1}, $q_1^* > 0, q_2^* > 0$ i.e. solution is indeed interior. Thus, equilibrium allocation is:
\begin{align*}
\begin{pmatrix}
\bar{z_1} - \frac{2\bar{z_2} - \bar{z_1}}{\frac{8}{2^{1/3}} - 1}\\
\\
\frac{\bar{z_1}}{2^{2/3}} - \frac{2\bar{z_2} - \bar{z_1}}{2^{2/3}8 - 2}
\end{pmatrix}, \begin{pmatrix}
\frac{2\bar{z_2} - \bar{z_1}}{\frac{8}{2^{1/3}} - 1}\\
\\
2^{1/3} \cdot \frac{2\bar{z_2} - \bar{z_1}}{4 - \frac{1}{2^{2/3}}}
\end{pmatrix}
\end{align*}
Assume now that $\frac{\bar{z_1}}{\bar{z_2}} > 2$ that means that the second firm shuts down. Hence
\begin{align*}
\begin{cases}
c_1(w) = p_1\\
\frac{a_{11}}{a_{21}} = \frac{\bar{z_1}}{\bar{z_2}}
\end{cases} \to \frac{2w_2}{w_1} = \frac{\bar{z_1}}{\bar{z_2}} \to w_1 = \frac{1}{3}\left(\frac{\bar{z_2}}{\bar{z_1}}\right)^{1/3}, w_2 = \frac{1}{6}\left(\frac{\bar{z_1}}{\bar{z_2}}\right)^{2/3}
\end{align*}
and the equilibrium allocation is
\begin{align*}
\begin{pmatrix}
\bar{z_1}\\
\bar{z_2}
\end{pmatrix}, \begin{pmatrix}
0\\
0
\end{pmatrix}
\end{align*}
Assume now that $\frac{\bar{z_1}}{\bar{z_2}} < \frac{1}{2}$ that means that the first firm shuts down. Hence
\begin{align*}
\begin{cases}
c_2(w) = p_2\\
\frac{a_{12}}{a_{22}} = \frac{\bar{z_1}}{\bar{z_2}}
\end{cases} \to \frac{w_2}{2w_1} = \frac{\bar{z_1}}{\bar{z_2}} \to w_1 = \frac{1}{6}\left(\frac{\bar{z_2}}{\bar{z_1}}\right)^{2/3}, w_2 = \frac{1}{3}\left(\frac{\bar{z_1}}{\bar{z_2}}\right)^{1/3}
\end{align*}
and the equilibrium allocation is
\begin{align*}
\begin{pmatrix}
0\\
0
\end{pmatrix},
\begin{pmatrix}
\bar{z_1}\\
\bar{z_2}
\end{pmatrix}
\end{align*}
\end{document}
